\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-12 paper/draft.tex
Update implementation

% \begin{lstlisting}[language=js,mathescape,upquote=true]
% //Input: module ID e.g., absolute filepath
% let load = function (ID) {
%   if (cache[ID]) {
%      return cache[ID];
%   }
%   let m = {
%     exports: {}, id: ID, dir: path.resolve(ID)
%   };
%   let cm = v8.compile(wrapped);
%   let ii = iris.getImplicit(ID);
%   let c = iris.freshContext(ii);
%   cm(m.exports, this.require, m, ID, m.dir, c);
%   let ei = iris.getExplicit(ID);
%   m.exports = iris.wrap(m.exports, [ei] );
%   cache[ID] = m;
%   return m.exports;
% }
% \end{lstlisting}

The \ttt{load} method in the \ttt{Module} module combines evaluation (line 10) and caching (line 14) of the wrapped module.
After evaluation, invoking the compiled function generates the value that is assigned to \ttt{module.exports} from within the module (line 12).
\sys passes a freshly constructed context at that invocation, modified according to the implicit segment of the (PIC??) corresponding to the module being loaded.
Before returning the value of \ttt{module.exports}, \sys transforms it according to the explicit segment of the (PIC??) corresponding to the module being loaded.
Finally, the results of the entire process are placed into the module cache for later use.

\subsection{Limitations}

% FIXME: Talk about the inability to 
A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
This is because \sys cannot transform the context of that file
As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).

\section{Evaluation and Experience}
\label{eval}

>>>>

% get second argument, no need to pass arguments around, tricky to 
% carefull hardcoding of paths, because \sys's code itself is split into modules
% We found it useful to add a function for white- and black-listing, as a set of regular expressions.
% Regular expressions where useful because internally libraries are identified via library identifiers that correspond to file-system paths.
% Originally intended as an aid to \sys's development and debugging, it proved useful enough for writing analysis A1--4 that decided to expose it to users.
% This is useful, for example, when...
% The configuration object accepts \ttt{only} and \ttt{not} that contain sets of regular expressions;

%% TODO: implementation
%% The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
%% These skeletons provide hooks for end-developers writing analyses.
%% Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
%% These hooks are then extended or rewritten by developers to

Fig.~\ref{fig:tx2}\emph{a--d} exemplifies our transformation techniques in the context of JavaScript.
\sys traverses a \ttt{Math} object, replaces functions such as \ttt{div} with wrappers; it also creates a modified version of the surrounding context and binds it to the library.
The precise wrappers depend on the intended analysis, reviewed next.

\subsection{Individual Analyses}
\label{impl2}

Individual analysis are implemented using a set of templates that provide initial constructs (see below).
\sys offers a small utility library to reduce boilerplate code for pattern-matching on types.
As a result, code that is specific to individual analyses averages about 20--30 lines.

\heading{Security Analysis}
To address the security concerns of third-party libraries, we develop a concrete \ttt{RWX} policy for analyzing accesses.
The language of the analysis is given in the following grammar:

\begin{alltt}
  str:  <identifier in JS>
  libs: [ str ]
  path: str `.` path
  mode: P{ R | W | X }
  body: { [ path: mode ]: path \(\in\) mods}
  analysis:  mods body
\end{alltt}

\heading{Performance Diagnosis}

\begin{equation}
\label{eq:2}
R_{new} =
\begin{cases}
  R +1, & \varrho\times\sum_{i=1}^t{w_il_i} > \delta + \delta_0  \\
  R -1,  & \varrho\times\sum_{i=1}^t{w_il_i}  < \delta + a * \delta_0
\end{cases}
\end{equation}

Scale-in (\ie $-1$) might not seem as important, but constrained environments benefit from quick re-allocation.
However, after scale-in, the system often ends up just scaling out the same module.
To avoid such oscillation, a small reclamation delay $a$ increases the system's confidence that the workload has moved away from a specific pattern.

% ATTRIBUTION
Interestingly, profiling functions running at each boundary cannot ``see through'' libraries in order to attribute load among a library and its dependencies correctly.
For example, an agent at the outermost boundary \ttt{A} of a dependency tree \ttt{A}$\rightarrow$\ttt{B}$\rightarrow$\ttt{C} does not know how much of the latency
% \eat{ is \ttt{A}-internal and how much}
comes from \ttt{B}. % or \ttt{B}'s dependency, \ttt{C}.

\heading{Invariant Discovery}
Describe specific type system

% \subsection{Limitations}
% 
% % FIXME: Talk about the inability to 
% A limitation of our implementation is that it cannot analyze the library importing \sys---usually, the top-level program entry-point equivalent to \ttt{main}.
% This is because \sys cannot transform the context of that file
% As a result, \sys as-is cannot be applied to, say, to analyze single-file programs---a common pattern in scripting languages often used for quick-and-dirty tasks.
% The simplest workaround here is to create an auxiliary file that imports \sys, and then import the single-file script (which, in most scripting languages would invoke it).

\section{Evaluation}
\label{eval}
